The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2016-02-14 script/en/script-en.tex
First version of CT Book ed 12. Most important point is the newly includes bitciphers chapter. Further things: Tried to reduce latex warnings amap. Changed wording from Sage to SageMath where visible...

\documentclass[a4paper,11pt,oneside]{book}
\overfullrule=5pt % uncomment to mark overfull boxes
\setlength{\fboxrule}{.5mm}
\setlength{\fboxsep}{1.75mm}
\setlength{\footnotesep}{6pt}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{fancyvrb}
\usepackage{makeidx}
\usepackage[pdftex]{graphicx}
\usepackage{pdfpages} %SR_2009: added new cover
%\usepackage{enumitem} %BE_2012: eliminate space after end{itemize} didn't work
\usepackage{paralist} %BE_2012: eliminate space after end{itemize} worked
                      %         with compactitem
\usepackage{arydshln} %BE_Jan2013: To use hdashline
\usepackage{verse}    %BE_Feb2013: To use \settowidth{\versewidth}{xxx}

\usepackage[flushmargin]{footmisc}
\usepackage{fullpage}
\usepackage[hyphens]{url} % options "hyphens" enables linebreaks in \url{}
% Literaturverzeichnis kapitelweise
\usepackage[labelstoglobalaux]{bibunits} % ohne labelstoglobalaux scheint man thebibilograpy und bibtex nicht mischen zu können
%\bibliographyunit[\section] % bibunits für das ganze Dokument aktivieren
\defaultbibliography{references}
\defaultbibliographystyle{abbrv}
\usepackage{float}
\usepackage{subfig}
\usepackage{shorttoc}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,bookmarksnumbered=true,pdfpagelabels,plainpages=false,hyperfootnotes=false]{hyperref}
%To reduce the number of hyperlink related 'pdfTeX warning's we use options 
%pdfpagelabels, plainpages=false and, hyperfootnotes=false and place hyperref after float.
%Option debug helps finding problems.

\floatstyle{boxed}
\newfloat{ctsquotefloat}{H}{loq}   % ctsQuotes-from-Books, List-of-Quotes
\floatname{ctsquotefloat}{Quote}   % ctsQuotes with centering
\newenvironment{ctsquote}{\begin{ctsquotefloat}\center}{\end{ctsquotefloat}}
\floatstyle{ruled}

\newfloat{sagecode}{!ht}{loc}[chapter]
\floatname{sagecode}{Sage sample}

@@

% \setlength{\textwidth}{460 pt}
% \hoffset-0.7in
\newtheorem{definition}{Definition}[section]
%\newcommand{\href}[2]{#2}
\newcommand{\hypertag}[2]{#1}
%\newcommand{\hyperlink}[2]{#2}
%\newcommand{\hypertarget}[2]{#2}
\newtheorem{theorem}{Theorem}[section]
\newenvironment{Proof}[1]{\noindent\textbf{Proof #1} \\}{\hfill$\Box$\par}
\newenvironment{example}[1]{\noindent\textbf{Example#1}}{}
\newenvironment{remark}[1]{\noindent\textbf{Comment#1}}{}

@@

% Define title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{ % Keine Leerzeilen, sonst Meldung: "Paragraph ended before \title was complete."
	{\Huge The CrypTool Script: \\
	 \vspace{5pt}
	 Cryptography, Mathematics, and More} \\
        \vspace{20pt}
	{\LARGE	Background reading for CrypTool\\ 
         the free e-learning program\\
	 (with number theory code samples for Sage)} \\
        \vspace{15pt}
        {\large (11th edition -- distributed with CrypTool version 1.4.31)}
        \vspace{180pt}
}

% Hier wird \vspace{32pt} einfach ignoriert
\author{ % Die Klammer zur Fontänderung funktioniert bei author nur einzeilig im Gegensatz zu title?!
        {\LARGE Copyright (c) Prof.\ Bernhard Esslinger (co-author and editor)}\\[5pt]
        {\LARGE and the CrypTool Team, 1998-2013}\\[5pt]
        {\LARGE Frankfurt am Main, Germany} \\*[15pt]
        \url{www.cryptool.org}
}

@@

\pagestyle{plain}
\setlength{\fboxrule}{.5mm}
\setlength{\fboxsep}{1.75mm}
\setlength{\footnotesep}{6pt}
\addtolength{\footskip}{8pt}
%\setlength{\footskip}{4cm}
%\renewcommand{\footnoterule}{\parindent0cm\rule{13cm}{.1pt}\vspace{.2cm}}
%Formatierung der Fu"snoten

%space between text and footnote 
\renewcommand\footnoterule{%
  \vspace{2em}%   <-- one line space between text and footnoterule
%\kern-3\p@
  \hrule width .4\columnwidth
 \vspace{4pt}
%kern 2.6\p@
}

%\long\def\@makefntext#1{%
%    \parindent 1em%
%    \noindent
%    \hbox to 1.8em{\hss\@makefnmark}#1}

@@

% Vergleichbar zur Nutzung von Texten aus der Wikipedia (=GNU Free Documentation Licence, GFDL)
% \vspace{200pt}
\begin{quote}
This is a free document, so the content of the document can
be copied and distributed, also for commercial purposes --- as long as
the authors, title and the CrypTool web site (\url{www.cryptool.org})
are acknowledged. Naturally, citations from the CrypTool script are
possible, as in all other documents.\\
Additionally, this document is liable to the specific license of the
GNU Free Documentation Licence.

    Copyright \copyright{} 1998--2013 Bernhard Esslinger and the
    CrypTool Team. Permission is granted to copy,
    distribute and/or modify this document under the terms of the GNU
    Free Documentation License, Version 1.3 or any later version
    published by the Free Software Foundation. A copy of
    the license is included in the section entitled
    \hyperlink{appendix-GNU-fdl}{``GNU Free Documentation License''}.

    This also includes the code of the Sage samples in this document.
\end{quote}

\vspace{420pt}
Source cover photograph: \url{www.photocase.com}, Andre Guenther\\

Typesetting software: \LaTeX

Version control software: Subversion

@@

%\parindent 0cm
% \parskip 4pt
% Setting the default for the vertical distance before a paragraph as distinguished variable
\newcounter{mycounterDefaultParskip}
\setcounter{mycounterDefaultParskip}{4}
\parskip \value{mycounterDefaultParskip} pt

\input{chapters/introduction.tex}

\mainmatter

\input{chapters/cryptomethods.tex}
\input{chapters/paper_and_pencil.tex}
\input{chapters/primes.tex}
\input{chapters/numbertheory.tex}
\input{chapters/moderncryptography.tex}
\input{chapters/digitalsignatures.tex}
\input{chapters/ellipticcurves.tex}
\input{chapters/homomorphicencryption.tex}
\bibliographyunit[\chapter]
\bibliography*{../de/references}
\bibliographystyle*{plain}
\input{chapters/crypto2020.tex}
\bibliographyunit

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\begin{appendix}
\newpage
\hypertarget{appendix-start}{}\label{s:appendix-start}
\chapter{Appendix}
    \begin{itemize}
      \item[1] \hyperlink{appendix-menu-overview-CT1}{CrypTool 1 Menu Tree}
      \item[2] \hyperlink{appendix-template-overview-CT2}{CrypTool 2 Templates}
      \item[3] \hyperlink{appendix-function-overview-JCT}{JCrypTool Functions}
      \item[4] \hyperlink{appendix-function-overview-CTO}{CrypTool-Online Functions}
      \item[5] \hyperlink{appendix-authors}{Bibliography of Movies and
                     Fictional Literature with Relation to Cryptography}
      \item[6] \hyperlink{appendix-Learn-NT}
                     {Learning Tool for Elementary Number Theory}
      \item[7] \hyperlink{appendix-using-sage}
                     {Using Sage with this Script}
      \item[8] \hyperlink{appendix-authors}{Authors of the CrypTool Script}
    \end{itemize}
  \newpage
  \input{chapters/menus.tex}
  \input{chapters/movies.tex}
  \input{chapters/what-is-sage.tex}
  \input{chapters/authors.tex}
\end{appendix}

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\begingroup
  % remove extra vertical space from \listoffigure and \listoftables so that 
  % it look similar to \listof{sagecode}
  %\setlength{\parskip}{0pt}
  \renewcommand*{\addvspace}[1]{}

@@

\clearpage\phantomsection
\addcontentsline{toc}{chapter}{List of Sage Code Examples}
\listof{sagecode}{List of Sage Code Examples}
\index{Sage!Code examples}
\label{sc:List-of-Sage-Code-Examples}

\vspace{30pt}
\begin{itemize}
  \item The source code of the Sage samples in this script is delivered as
        Sage program files within the CrypTool-1 setup program.
        All samples within one chapter are collected in one file.
        After installing CrypTool 1 \index{CrypTool 1} you find
        the Sage samples within the subdirectory \verb#sage# in the
        following 4 files:\\
        - SAGE-Samples-in-Chap01.sage \\
        - SAGE-Samples-in-Chap02.sage \\
        - SAGE-Samples-in-Chap03.sage \\
        - SAGE-Samples-in-Chap04.sage
  \item All samples have been tested with Sage Version 5.3 (Release Date 2012-09-08).
\end{itemize}

>>>>

\documentclass[a4paper,11pt,oneside]{book}
\overfullrule=5pt
\usepackage[latin1]{inputenc}
\DeclareTextSymbolDefault{\dh}{T1}
\DeclareTextSymbolDefault{\textperthousand}{T1}

\usepackage{datetime} % To distinguish often compiled draft versions

\setlength{\fboxrule}{.5mm}
\setlength{\fboxsep}{1.75mm}
\setlength{\footnotesep}{6pt}

\usepackage{amsmath}
\usepackage{amssymb,amscd,latexsym}   %BERM2: added for biciphers.tex
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{color}

\usepackage{fancyvrb}
\usepackage{makeidx}
\usepackage[pdftex]{graphicx}
\usepackage{pdfpages}
\usepackage{paralist}
\usepackage{arydshln}
\usepackage{verse}

\usepackage[flushmargin]{footmisc}
\usepackage{fullpage}
\usepackage[hyphens]{url}
\appto\UrlBreaks{\do\a\do\b\do\c\do\d\do\e\do\f\do\g\do\h\do\i\do\j
\do\k\do\l\do\m\do\n\do\o\do\p\do\q\do\r\do\s\do\t\do\u\do\v\do\w
\do\x\do\y\do\z}

\usepackage[labelstoglobalaux]{bibunits}
%\bibliographyunit[\section] % bibunits für das ganze Dokument aktivieren
\defaultbibliography{references} % Why only in English version?
\defaultbibliographystyle{abbrv} % Why only in English version?

\usepackage{float}
\usepackage{subfig}
\usepackage{shorttoc}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,bookmarksnumbered=true,pdfpagelabels,plainpages=false,hyperfootnotes=false]{hyperref}

\floatstyle{boxed}
\newfloat{ctsquotefloat}{H}{loq}
\floatname{ctsquotefloat}{Quote}
\newenvironment{ctsquote}{\begin{ctsquotefloat}\center}{\end{ctsquotefloat}}
\floatstyle{ruled}

\newfloat{sagecode}{!ht}{loc}[chapter]
\floatname{sagecode}{SageMath sample}

@@

%\newcommand{\href}[2]{#2}
\newcommand{\hypertag}[2]{#1}
%\newcommand{\hyperlink}[2]{#2}
%\newcommand{\hypertarget}[2]{#2}

\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\renewenvironment{proof}[1]{\noindent\textbf{Proof #1} \\}{\hfill$\Box$\par}  %BERM: Instead of making AMS-Theorem a comment in order to have no redefinition of proof, used renewenvironment [proof used in moderncryptography.text and primes.text]. Necessary only in English!
\newenvironment{example}[1]{\noindent\textbf{Example#1}}{}
\newenvironment{remark}[1]{\noindent\textbf{Comment#1}}{}

\newenvironment{ Latex_Create-Closed-Dummy-Environ }{}{}

@@

% Define title ..............
\title{ % Keine Leerzeilen, sonst Meldung: "Paragraph ended before \title was complete."
	{\Huge The CrypTool Book \\[15pt]
         Cryptography, Mathematics, and More} \\[25pt]
	{\LARGE	Background reading for CrypTool\\ 
         the free e-learning crypto program \\[5pt]
	 (with code samples written in SageMath)} \\[25pt]
	{\large 12th edition -- draft version (\settimeformat{hhmmsstime}\currenttime)}
	% {\large 12th edition}
        \vspace{180pt}
}

\author{
        {\LARGE Prof.\ Bernhard Esslinger (co-author and editor)}\\[10pt]
        {\LARGE and the CrypTool Team, 1998-2016}\\[10pt]
        {\LARGE Frankfurt am Main, Germany} \\*[15pt]
        \url{www.cryptool.org}
}

@@

\pagestyle{plain}
\setlength{\fboxrule}{.5mm}
\setlength{\fboxsep}{1.75mm}
\setlength{\footnotesep}{6pt}
\addtolength{\footskip}{8pt}

\renewcommand\footnoterule{%
  \vspace{2em}
  \hrule width .4\columnwidth
 \vspace{4pt}
}

@@

\begin{quote}
This is a free document, so the content of the document can
be copied and distributed, also for commercial purposes --- as long as
the authors, title and the CrypTool web site (\url{www.cryptool.org})
are acknowledged. Naturally, citations from the CrypTool script are
possible, as in all other documents.\\
Additionally, this document is liable to the specific license of the
GNU Free Documentation Licence.

    Copyright \copyright{} 1998--2016 Bernhard Esslinger and the
    CrypTool Team. Permission is granted to copy,
    distribute and/or modify this document under the terms of the GNU
    Free Documentation License, Version 1.3 or any later version
    published by the Free Software Foundation. A copy of
    the license is included in the section entitled
    \hyperlink{appendix-GNU-fdl}{``GNU Free Documentation License''}.

    This also includes the code of the SageMath samples in this document.
\end{quote}

\vspace{420pt}
\noindent
Source cover photograph: \url{www.photocase.com}, Andre Guenther\\
Typesetting software: \LaTeX\\
Version control software: Subversion

@@

\newcounter{mycounterDefaultParskip}
\setcounter{mycounterDefaultParskip}{4}
\parskip \value{mycounterDefaultParskip} pt

\input{chapters/introduction.tex}
\mainmatter
\input{chapters/cryptomethods.tex}
\input{chapters/paper_and_pencil.tex}
\input{chapters/primes.tex}
\input{chapters/numbertheory.tex}
\input{chapters/moderncryptography.tex}
\input{chapters/digitalsignatures.tex}
\input{chapters/ellipticcurves.tex}
\input{chapters/bitciphers.tex}
\input{chapters/homomorphicencryption.tex}
\bibliographyunit[\chapter]
\bibliography*{../de/references}
\bibliographystyle*{plain}
\input{chapters/crypto2020.tex}
\bibliographyunit

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\begin{appendix}
\newpage
\hypertarget{appendix-start}{}\label{s:appendix-start}
\chapter{Appendix}
    \begin{itemize}
      \item[1] \hyperlink{appendix-menu-overview-CT1}{CrypTool 1 Menu Tree}
      \item[2] \hyperlink{appendix-template-overview-CT2}{CrypTool 2 Templates}
      \item[3] \hyperlink{appendix-function-overview-JCT}{JCrypTool Functions}
      \item[4] \hyperlink{appendix-function-overview-CTO}{CrypTool-Online Functions}
      \item[5] \hyperlink{appendix-authors}{Bibliography of Movies and
                     Fictional Literature with Relation to Cryptography}
      \item[6] \hyperlink{appendix-Learn-NT}
                     {Learning Tool for Elementary Number Theory}
      \item[7] \hyperlink{appendix-using-sage}
                     {Short Introduction into the Computer Algebra System SageMath}
      \item[8] \hyperlink{appendix-authors}{Authors of the CrypTool Script}
    \end{itemize}
  \newpage
  \input{chapters/menus.tex}
  \input{chapters/movies.tex}
  \input{chapters/what-is-sage.tex}
  \input{chapters/authors.tex}
\end{appendix}

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\begingroup
  %\setlength{\parskip}{0pt}
  \renewcommand*{\addvspace}[1]{}

@@

\clearpage\phantomsection
\addcontentsline{toc}{chapter}{List of SageMath Code Examples}
\listof{sagecode}{List of SageMath Code Examples}
\index{SageMath!Code examples}
\label{sc:List-of-Sage-Code-Examples}

\vspace{30pt}
\begin{itemize}
  \item The source code of the SageMath samples in this script is delivered as
        SageMath program files within the CrypTool-1 setup program.
        All samples within one chapter are collected in one file.
        After installing CrypTool 1 \index{CrypTool 1} you find
        the SageMath samples within the subdirectory \verb#sagemath# in the
        following 4 files:\\
        - SageMath-Samples-in-Chap01.sage \\
        - SageMath-Samples-in-Chap02.sage \\
        - SageMath-Samples-in-Chap03.sage \\
        - SageMath-Samples-in-Chap04.sage
  \item All samples have been tested with SageMath Version 5.3 (Release Date 2012-09-08)xxxxxxxxxxxxxxxxxxxxxxxxxxx.
\end{itemize}
